The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-04 paper/ms.tex
bedding revisions complete

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6}$
Timothy R. White,$^{7,5}$\newauthor
Amalie Stokholm,$^{5}$
Allyson Bieryla,$^{8}$
David W. Latham,$^{8}$
Conny Aerts,$^{9,10,11}$\newauthor
Suzanne Aigrain,$^{3}$ 
Victoria Antoci,$^{5}$
Timothy R. Bedding,$^{12,5}$
Dominic M. Bowman,$^{10}$\newauthor
Ashley Chontos,$^{13}$
Gilbert A. Esquerdo,$^{8}$
Daniel Huber,$^{13,14,8}$
Paula Jofr\'{e},$^{15}$\newauthor
Madeline Lucy,$^{6}$
Simon Murphy,$^{12,5}$
Timothy van Reeth,$^{12,5}$\newauthor
Victor Silva Aguirre,$^{5}$
Jie Yu$^{12,5}$ 
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{8}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{9}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{10}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{11}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
$^{12}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{14}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
$^{15}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

@@

% Abstract of the paper
\begin{abstract}
Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this Paper, we focus in particular on a subset of these consisting of 66~red giants for which we detect solar-like oscillations. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C}. It has yielded the detection of gravity-mode period spacings in a red giant \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation of red giants \citep{rggmoderotation,2012A&A...548A..10M} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of main-sequence stars as cool as the Sun and hotter \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main sequence. 
\newpage

A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}. Asteroseismological studies with \kepler complement other probes of stellar physics well: for example, the APOKASC sample of~1916 spectroscopically- and asteroseismically-characterized red giant stars \citep{2014ApJS..215...19P}. For this APOKASC sample, \citet{hawkinsapogee} have been able to extract precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values. It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark}, parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}. This is especially important in the context of the \gaia mission \citep{gaia}, which has recently put out its second data release of 1,692,919,135 sources, including 1,331,909,727 with parallaxes \citep{gaiadr2}. These data will form the basis of many large surveys and it is vital that they are calibrated correctly. To this end, 34~FGK stars including both giants and dwarfs have been chosen as \gaia-ESO benchmark stars for which metallicities \citep{gaiabenchmark1}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined. This includes only four main sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology. This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}. Furthermore, by combining asteroseismology with optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo from these collateral data, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only one~G dwarf. We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 34~red giants. We do not model main sequence stars in great detail, but provide some discussion and initial classification of interesting variability. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES). For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, the majority of which were previously entirely missing. Sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.

Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram using \gaia $Bp-Rp$ and absolute~$G$ magnitudes and \gaia~DR2 calibrated distances \citep{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the remainder of the \kepler sample.

We identify the evolutionary state of stars in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}. Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 66 of these stars as evolved systems, and the remaining~36 lie apparently on the main sequence.

The coolest main sequence star, BD+43~3068, is a G0 dwarf with a $G$ magnitude of 8.3 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a solar analogue. It is possible that it was previously misidentified as a giant. Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star. Its light curve shows neither rotational modulation (as determined by its featureless autocorrelation) nor evidence for transits.

Considering stars lying close to the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants.

@@

In preparing light curves of the \kepler smear stars, we have followed the methods described in \citet{smear}, with some improvements. We selected our input RA and Dec values from the \kepler Input Catalog (KIC) \citep{kic}, and queried MAST to find the corresponding mean pixel position for a given \kepler quarter. We then measured the centroid of smear columns in the vicinity, and used these values to do raw aperture photometry. We found that the cosine-bell aperture used for raw photometry in \citet{smear} can in some light curves introduce position-dependent systematics and jumps. We instead in this work have applied a super-Gaussian aperture, $A \propto \exp{\dfrac{-(x-x_0)}{w} ^ 4}$, where $x_0$ is the centroid and $w$ a width in pixels. The very flat top of this function helps avoid significant variation with position, while still smoothly rolling off at the edges to avoid discontinuous artefacts. This is calculated on a grid of $10\,\times$ subsampled points in pixel space so that the sharply varying edge changes column weights smoothly as a function of centroid. We have then extracted photometry using apertures with a range of widths $w \in\{1.5,~2,~3,~4,~5\}$ pixels.

From this raw photometry a background light curve was subtracted, which corrects for time-varying global systematics. Whereas in \citet{smear} we subtracted a background estimate chosen manually, for this larger set of light curves, we have now chosen the lowest $25\%$ of pixels by median flux as being unlikely to be contaminated by stars, and taken our background level to be the median of this at each time sample. To denoise this, we fit a Gaussian Process with a 30-day timescale squared exponential kernel using \textsc{george} \citep{hodlr}, and our final background light curve is taken to be the posterior mean of this GP.

The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue which is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}. We have adopted the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of either the first~4 or~8 CBVs to each light curve. This can subtract astrophysical signals on long timescales, such that we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, or indeed raw uncorrected lightcurves for stars variable at high amplitude on $\sim$~quarter timescales, but otherwise we recommend the 8~CBV light curves. There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper. In the following, we will use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} implementation \citep{k2sc}. This is not necessarily the optimal choice for all red giants, especially those with oscillations on a 6.5~h timescale, but is a reasonable proxy nevertheless for white noise and leads to satisfactory results upon visual inspection of the present sample.

@@

Because the smear data are collected along an entire CCD~column, there is the risk of contamination from other bright stars. This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter. We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and both visually inspected these for significant differences. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In order to better quantify this, we compute the inner product of  normalized periodograms of the odd and even quarters each smoothed with a 3-element Gaussian kernel. If this overlap integral is 1, then the power spectra are identical; substantial departures from unity may be caused by real nonstationary or long-period stellar variation, noise, or gain or contamination differences between the seasons. We find that the distribution of overlaps is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$. We investigate these further, finding that in not all of these cases is there an obvious problem, for example the classical pulsator HD~175841 in which amplitudes of several pulsations have changed but the overall distribution seems very similar, in which we conclude that the variation is probably astrophysical or an artefact of our data processing.

@@

\caption{\label{contamination2}
Histogram over overlap integrals of smoothed periodograms of odd and even quarters for each star in the sample. The peak at $\sim 0.91$ contains normal stars with limited contamination; we investigate the 22 stars with overlaps below 0.9 for which there is a significant risk of contamination.}
\end{figure}

@@

Among the~66 red giants identified in this sample, for~32 the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs), without specifically meaning these are LPVs by a particular astrophysical definition, and they are discussed further in Section~\ref{lpvs}. For the~34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters through the approximate scaling relations:

@@

\begin{equation}
\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{M {R}^{-3}}
\end{equation}

We have followed the method of \citet{2016AN....337..774D}, obtaining a Lomb-Scargle periodogram of the smoothed time series according to the method of \citet{2011MNRAS.414L...6G}. The posterior distribution of the asteroseismic parameters is obtained with a Markov Chain Monte Carlo fit to the smoothed periodogram, applying the combined granulation and oscillation model of \citet{2014A&A...570A..41K}. This consists of two Harvey profiles for the granulation \citep{1985ESASP.235..199H}, a Gaussian envelope for the stellar oscillations, and a white noise background for instrumental noise. The marginal posterior distribution for the oscillation envelope is well-approximated by a single Gaussian, and we have taken its median and standard deviation to be our estimates for \numax and its uncertainty.

To estimate \Dnu, we have divided the power spectrum through by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax. In practice, for this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian as with \numax.

>>>>

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6}$
Timothy R. White,$^{7,5}$\newauthor
Amalie Stokholm,$^{5}$
Allyson Bieryla,$^{8}$
David W. Latham,$^{8}$
Conny Aerts,$^{9,10,11}$\newauthor
Suzanne Aigrain,$^{3}$ 
Victoria Antoci,$^{5}$
Timothy R. Bedding,$^{12,5}$
Dominic M. Bowman,$^{10}$\newauthor
Ashley Chontos,$^{13}$
Gilbert A. Esquerdo,$^{8}$
Daniel Huber,$^{13}$
Paula Jofr\'{e},$^{14}$\newauthor
Madeline Lucey,$^{6}$
Simon J. Murphy,$^{12,5}$
Timothy van Reeth,$^{12,5}$\newauthor
Victor Silva Aguirre,$^{5}$
Jie Yu$^{12,5}$ 
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{8}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{9}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{10}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{11}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
$^{12}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{14}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

@@

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this Paper, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C}. It has yielded the detection of gravity-mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2016MNRAS.456.2183D,2018MNRAS.479.4786V}. %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence.

A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2,silvaplanetages,2016MNRAS.456.2183D}. Asteroseismological studies with \kepler complement other probes of stellar physics well: for example, the APOKASC sample of~1916 spectroscopically- and asteroseismically-characterized red giant stars \citep{2014ApJS..215...19P}. For this APOKASC sample, \citet{hawkinsapogee} have been able to extract precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values. It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark}, parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}. This is especially important in the context of the \gaia mission \citep{gaia}, which has recently put out its second data release of 1,692,919,135 sources, including 1,331,909,727 with parallaxes \citep{gaiadr2}. These data will form the basis of many large surveys and it is vital that they are calibrated correctly. To this end, 34~FGK stars including both giants and dwarfs have been chosen as \gaia-ESO benchmark stars for which metallicities \citep{gaiabenchmark1}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined. This includes only four main-sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology. This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}. Furthermore, by combining asteroseismology with optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo from these collateral data, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only one~G dwarf. We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 34~red giants. We do not model main-sequence stars in great detail, but provide some discussion and initial classification of interesting variability. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES). For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

We selected all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters. The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$, together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars were not on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.

Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram using \gaia $Bp-Rp$ and absolute~$G$ magnitudes and \gaia~DR2 calibrated distances \citep{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram selected to have higher apparent brightnesses than the general \kepler population, appear also to have higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared to \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the majority of the \kepler sample.

We identify the evolutionary state of main-sequence versus evolved stars from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}. Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 66 of these stars as evolved systems, and the remaining~36 lie on the main-sequence.

The coolest main-sequence star, BD+43~3068 (SAO~47785), is a G0 dwarf with a $G$ magnitude of 8.3 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a solar analogue. It is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star. Its light curve shows neither rotational modulation (as determined by its featureless autocorrelation) nor evidence for transits.

Considering stars lying close to the main-sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants.

@@

In generating light curves of the \kepler smear stars, we have followed the methods described by \citet{smear}, with some improvements. We selected our input RA and Dec values from the \kepler Input Catalog (KIC) \citep{kic}, and queried MAST to find the corresponding mean pixel position for each \kepler quarter. We then measured the centroid of smear columns in the vicinity, and used these values to do raw aperture photometry. We found that the cosine-bell aperture used for raw photometry by \citet{smear} can sometimes introduce position-dependent systematics and jumps. We instead used a super-Gaussian aperture, $A \propto \exp{\dfrac{-(x-x_0)}{w} ^ 4}$, where $x_0$ is the centroid and $w$ is the width in pixels. The very flat top of this function helps avoid significant variation with position, while still smoothly rolling off at the edges to avoid discontinuous artefacts. The super-Gaussian is calculated on a grid of $10\,\times$ subsampled points in pixel space so that the sharply varying edge changes column weights smoothly as a function of centroid. We then extracted photometry using apertures with a range of widths $w \in\{1.5,~2,~3,~4,~5\}$ pixels.

From this raw photometry a background light curve was subtracted, correcting for time-varying global systematics. Whereas in \citet{smear} we subtracted a background estimated manually, for this larger set of light curves, we have chosen the lowest $25\%$ of pixels by median flux as being unlikely to be contaminated by stars, and taken our background level to be the median of this at each time sample. To reduce the noise in this background model, we fitted a Gaussian Process with a 30-day timescale squared exponential kernel using \textsc{george} \citep{hodlr}, and our final background light curve is taken to be the posterior mean of this GP.

The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue that is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}. We have adopted the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of either the first~4 or~8 CBVs to each light curve. This can remove astrophysical signals having long timescales, and so we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, or indeed raw uncorrected lightcurves for stars variable at high amplitude on $\sim$~quarter timescales, but otherwise we recommend the 8~CBV light curves. There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper. In the following, we use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} CDPP implementation \citep{k2sc}. This is not necessarily the optimal choice for all red giants, especially those with oscillations on a 6.5~h timescale, but is a reasonable proxy for white noise and leads to satisfactory results upon visual inspection of the present sample.

@@

Because the smear data are collected along an entire CCD~column, there is the risk of contamination from other bright stars. This is especially true when doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter. We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, after clipping for outliers. We consider only odd and even quarters separately, and also the full combined time series. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In order to better quantify this, we computed the inner product of normalized periodograms of the odd and even quarters, each smoothed with a 3-element Gaussian kernel. If this overlap integral is 1, then the power spectra are identical; substantial departures from unity may be caused by real nonstationary or long-period stellar variation, noise, or gain or contamination differences between the seasons. We found that the distribution of overlaps (Figure~\ref{contamination2}) is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$. We investigate these further, finding that in some of these cases  there was no obvious problem. For example, the classical pulsator HD~175841 showed amplitude changes of several pulsations but the overall distribution seemed very similar, from which we conclude that the variation is probably astrophysical.

@@

\caption{\label{contamination2}
Histogram over overlap integrals of smoothed periodograms of odd and even quarters for each star in the sample. The peak at $\sim 0.91$ contains normal stars with limited contamination; we investigate the 22 stars with overlaps below 0.9 for which there is a significant possibility of contamination.}
\end{figure}

@@

Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics and systematics correction. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs). For the~34 giants for with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters through the approximate scaling relations:

@@

\begin{equation}
\label{Dnuscaling}
\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{M {R}^{-3}}
\end{equation}

We have followed the method of \citet{2016AN....337..774D}, obtaining a Lomb-Scargle periodogram of the smoothed time series according to the method of \citet{2011MNRAS.414L...6G}. The posterior distribution of the asteroseismic parameters was obtained with a Markov Chain Monte Carlo fit to the smoothed periodogram, applying the combined granulation and oscillation model of \citet{2014A&A...570A..41K}. This consists of two Harvey profiles for the granulation \citep{1985ESASP.235..199H}, a Gaussian envelope for the stellar oscillations, and a white noise background for photon noise. The marginal posterior distribution for the oscillation envelope is well-approximated by a single Gaussian, and we have taken its median and standard deviation to be our estimates for \numax and its uncertainty.

To estimate \Dnu, we divided the power spectrum by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax. For this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian.
